Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-07-10 manuscripts/reply/reply-abstract.tex
Working on overhaul of intro for reply ms.

Biogeographers frequently seek to explain population and species
differentiation on geographical phenomena.
Establishing that a set of population splitting events occurred
at the same time can be a potentially persuasive argument that a set of taxa
were affected by the same geographic events.
Unfortunately, estimating divergence times precisely when one lacks
precise information about the rate of molecular evolution is a notoriously
difficult problem in evolutionary biology.
\citet{Huang2011} introduced an approximate Bayesian approach (implemented
in the software \msb) which can be used to estimate the probabilities of
models in which multiple sets of taxa diverge at the same time. 
% This method  does not require a common set of character data that links all
% of the taxa under investigation, but does require the relative mutation
% rates among the taxa and loci to be assumed \emph{a priori}.
Recently, \citet{Oaks2012} used this model-choice framework to 
study 22 pairs of vertebrate lineages which are distributed across
the Philippines; they also studied the behavior of the \msb approach
using computer simulations.
\citet{Oaks2012} found the method was very sensitive to prior assumptions and
had low power to detect variation in divergence times.
These results were not surprising, in light of a rich statistical literature
showing that the marginal likelihood of a model is sensitive to the
use of vague priors.
Because this sensitivity to prior assumptions affects the crucial insights 
that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
that users of the approach should carefully assess the robustness of their 
conclusions to different priors.
According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
was due to excessively broad priors on divergence times, leading to 
inadequate numbers of simulation replicates.
They proposed a new model-averaging approach that uses narrow, empirically
informed uniform priors.
Here we demonstrate that the approach of \citet{Hickerson2013} is
dangerous in the sense that the empirically-derived priors often
exclude from consideration the true values of the models' parameters.
On a more fundamental level, we question the value of adopting an empirical
Bayesian stance for this model-choice problem, because it can mislead model
posterior probabilities, which are inherently measures of belief in the
models after prior knowledge is updated by the data.
The robust Bayesian approach of conducting analyses under a variety
of priors can reveal prior sensitivity and communicate which assumptions
underlie model inference.
Furthermore, simulations provide insight into the temporal resolution of the
method, which helps guide interpretation of results.

>>>>

Biogeographers frequently seek to explain population and species
differentiation on geographical phenomena.
Establishing that a set of population splitting events occurred
at the same time can be a potentially persuasive argument that a set of taxa
were affected by the same geographic events.
Unfortunately, estimating divergence times precisely when one lacks
precise information about the rate of molecular evolution is a notoriously
difficult problem in evolutionary biology.
\citet{Huang2011} introduced an approximate Bayesian approach (implemented
in the software \msb) which can be used to estimate the probabilities of
models in which multiple sets of taxa diverge at the same time. 
% This method  does not require a common set of character data that links all
% of the taxa under investigation, but does require the relative mutation
% rates among the taxa and loci to be assumed \emph{a priori}.
Recently, \citet{Oaks2012} used this model-choice framework to 
study 22 pairs of vertebrate lineages which are distributed across
the Philippines; they also studied the behavior of the \msb approach
using computer simulations.
\citet{Oaks2012} found the method was very sensitive to prior assumptions and
had low power to detect variation in divergence times.
These results were not surprising, in light of a rich statistical literature
showing that the marginal likelihood of a model is sensitive to the
use of vague priors.
Because this sensitivity to prior assumptions affects the crucial insights 
that a researcher who employs \msb seeks to gain, \citet{Oaks2012} recommended
that users of the approach should carefully assess the robustness of their 
conclusions to different priors.
According to \citet{Hickerson2013}, the lack of robustness in \msb analyses
was due to excessively broad priors on divergence times leading to 
inadequate numbers of simulation replicates.
They proposed a new model-averaging approach that uses narrow, empirically
informed uniform priors.
Here we demonstrate that the approach of \citet{Hickerson2013} is
dangerous in the sense that the empirically-derived priors often
exclude from consideration the true values of the models' parameters.
On a more fundamental level, we question the value of adopting an empirical
Bayesian stance for this model-choice problem, because it can mislead model
posterior probabilities, which are inherently measures of belief in the
models after prior knowledge is updated by the data.
The robust Bayesian approach of conducting analyses under a variety
of priors can reveal prior sensitivity and communicate which assumptions
underlie model inference.
Furthermore, simulations provide insight into the temporal resolution of the
method, which helps guide interpretation of results.

### 2014-07-10 manuscripts/reply/reply-main.tex
Working on overhaul of intro for reply ms.

\section{Introduction}

\msb \citep{Huang2011} uses approximate Bayesian computation (ABC) to estimate
the distribution of divergence times among co-distributed pairs of taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
% A full description of the model is given in \citet{Oaks2012}.
% Frequently, the exact values of the divergence times are hard 
% to determine because researchers typically lack precise knowledge 
% of the rate at which substitutions occur.
% The exact divergence time is therefore often viewed as a nuisance parameter,
% and researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       support for models with few divergence events shared across taxa. Thus,
       the primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

This is not surprising given the rich statistical literature that shows that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
\change{
% By using such priors on divergence times, we are essentially telling the
% method to favor models with few divergence times even if they do not
% explain the data very well.
This affect of the priors on marginal likelihoods creates a penalty for
over-parameterization in Bayesian model choice.
However, for this inference problem, the uniform priors on divergence times can
create a strong preference for simple models that are often of interest to
biogeographers even if these models do not explain the data very well.
This phenomenon is extrinsic to the numerical approximation machinery of \msb;
with such prior assumptions, the true posterior will favor models with
few divergence events.
However, such results, even if correct from the perspective of Bayesian model
choice, do not provide the biogeographical insights that a researcher who
employs \msb seeks to gain.
For example, a biogeographer would like to interpret the posterior probability
of a simultaneous divergence model as an estimate of the probability that this
model is correct.
However, when such prior assumptions are made about divergence times, the
estimated posterior probability is better interpretted as the probability that
you cannot completely rule out that the simultaneous-divergence model can
explain the data.
% Note, this is a statistical issue, extrinsic to \msb, and does not question the
% soundness of the numerical approximation machinery of \msb.
}

\citet{Hickerson2013} suggest the problem is the result of a numerical issue
intrinsic to \msb, concluding the method's rejection algorithm is inefficient
and will be biased toward models with fewer divergence-time parameters, because
the parameter space of these models are more densely sampled relative to models
with more divergence-time parameters.
We agree that sampling error is present in all numerical Bayesian estimation
methods, however, we show here that it is not a major contributer to the
biases found by \citet{Oaks2012}.
We present results here of analyses that, when combined with the results
of \citet{Oaks2012}, strongly suggest that \msb prefers models with few
divergence-time parameters, because they have greater likelihoods when
averaged over broad uniform priors on divergences times.

\citet{Oaks2012} suggest alternative prior probability distributions on
divergence-times could increase the marginal likelihoods of models with more
divergence-time parameters and thus reduce spurious support for models of
temporally clustered divergences.
Alternatively, \citet{Hickerson2013} present an approach that uses empirically
informed uniform priors and Bayesian model-averaging in an attempt to accommodate
uncertainty in selecting priors.
In general, we agree with the use of Bayesian model averaging to obtain a
posterior estimate marginalized over uncertainty in prior choice.
However, we question whether adding an additional dimension of model choice
that samples over empirically informed uniform priors is a fruitful solution
for a model-choice method that is highly sensitive to priors.

\change{
In this paper, we discuss theoretical and practical considerations of using
empirically informed priors for Bayesian model choice.
}
Furthermore, we evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
Here, we avoid this error, but still find their approach to be biased toward
clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
\change{
Our results, show that it is difficult to choose a uniformly distributed prior
on divergence times that is broad enough to confidently contain the true values
of parameters while being narrow enough to avoid spurious support of models
with less parameter space.
}
However, recent work shows more flexible probability distributions without a
hard upper bound (e.g., gamma) can accommodate prior uncertainty in divergence
times without inhibiting the marginal likelihoods of models with more
divergence-time parameters, and as a result, increase the method's power to
detect temporal variation in divergences
\citep{Oaks2014dpp}.

\section{The potential implications of empirical Bayesian model choice}
\change{
The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
highly sensitive to the prior on divergence times.
Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
divergences when using a prior on divergence times that is strongly
informed by the data being analyzed.
The main argument of \citet{Hickerson2013} is that the priors used by
\citet{Oaks2012} were not informative enough.
}
%
% \citet{Hickerson2013} repeatedly refer to the prior distributions used by
% \citet{Oaks2012} for divergence-time parameters as ``poorly selected.''
% However, this is misleading, as \citet{Oaks2012} discuss in detail how they
% selected their prior to reflect the large amount of uncertainty about the
% timing of divergences across all 22 of the taxa in their study (see section
% ``Specifying and simulating the joint prior'' of \citet{Oaks2012}).
% \citet{Oaks2012} further discuss how the use of uniform prior distributions in
% \msb for many of the model's parameters requires investigators to select broad
% priors to avoid excluding the truth \textit{a priori}, resulting in too much
% density in improbable regions of parameter space.

% \citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
% data to inform their prior on divergence times (i.e., an empirical Bayesian
% approach).
% However, \citet{Oaks2012} did use empirically informed priors to mimic
% empirical situations in which a large amount of prior information is available;
% they did so to assess the prior sensitivity of the method and to determine if
% uniform priors in such situations are narrow enough to avoid spurious support
% of models with few divergence-time parameters.
% The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
% highly sensitive to the prior on divergence times.
% Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
% divergences under the empirically informed priors.
%
% The main argument of \citet{Hickerson2013} is that the priors used by
% \citet{Oaks2012} were not informative enough.
They suggest a very narrow, highly informed uniform prior on divergence times
is necessary to avoid the method's preference for models with few
divergence-time parameters.
Such an empirical Bayesian approach to model selection raises some theoretical
and practical concerns, some of which were discussed by \citet{Oaks2012} (see
the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}); we expand on this here.

@@

\subsection{Practical concerns about empirically informed uniform priors for
    Bayesian model choice}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors.
% for a method that has already been shown to be biased toward models with less
% parameter space.
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa.
%, a major problem when using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
some of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).

\change{
Hickerson et al.'s \citeyear{Hickerson2013} results that strongly prefer the
narrowest priors on divergence times (their $M_1$ and $M_2$) suggest their
approach is biased toward models with less parameter space, and as a
consequence, will estimate model-averaged posteriors dominated by models that
exclude true values of model's parameters.
}
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging
approach of \citet{Hickerson2013}, but set one of the prior models with a
uniform prior on divergence times that is unrealistically narrow, and almost
certainly excludes most, if not all, of the true divergence times of the 22
taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

\subsubsection{Simulation-based assessment of Hickerson et al.'s
\citeyear{Hickerson2013} model averaging over empirical priors}

@@

Even if we assume the gene divergence times are estimated without error,
Hickerson et al.'s \citeyear{Hickerson2013} argument only applies to one of the
three different priors used by \citet{Oaks2012}.
The narrowest prior on divergence times used by \citet{Oaks2012} ($U(0, 5)$)
closely mirrors the range of estimates of gene-divergence times if we assume
the same mutation rate and one generation per year (0--5 million years ago).
Applying Hickerson et al.'s (\citeyear{Hickerson2013}) sampling-probability
argument demonstrates this prior is densely populated with samples with large
numbers of divergence parameters with values younger than the estimated gene
divergence estimates.
Thus, if insufficient prior sampling is to blame for the bias, it should be
much reduced under the narrow prior on \divt{}.
However, the magnitude of the bias is very similar across all three priors
explored by \citet{Oaks2012}.
\citet{Hickerson2013} point out a case where the narrow prior performs
slightly better (panel L of Figures S32, S37, and S38 of \citet{Oaks2012}).
However, it is important to note that these results suffered from a bug
in \msb, and there are many cases after \citet{Oaks2012} corrected the 
bug where the narrow prior performs slightly worse (see panels D--J of
Figures 3 and S12).

>>>>

\section{Introduction}
Biogeographers frequently seek to explain population and species
differentiation on geographical phenomena.
Establishing that a set of population splitting events occurred
at the same time can be a potentially persuasive argument that a set of taxa
were affected by the same geographic events.
% Unfortunately, estimating divergence times precisely when one lacks
% precise information about the rate of molecular evolution is a notoriously
% difficult problem in evolutionary biology.
\citet{Huang2011} introduced an approximate Bayesian approach (implemented
in the software \msb) which can be used to estimate the probabilities of
models in which multiple sets of taxa diverge at the same time. 
% This method  does not require a common set of character data that links all
% of the taxa under investigation, but does require the relative mutation
% rates among the taxa and loci to be assumed \emph{a priori}.

Recently, \citet{Oaks2012} used this model-choice framework to 
study 22 pairs of vertebrate lineages which are distributed across
the Philippines; they also studied the behavior of the \msb approach
using computer simulations.
They found the method was very sensitive to prior assumptions and suggested
this was due to the fact that the marginal likelihoods of models are sensitive
to the use of uniform priors on divergence times.
In response, \citet{Hickerson2013} suggested the lack of robustness in \msb
analyses was caused by sampling error due to the inefficiency of the method's
rejection algorithm.
They proposed a model-averaging approach that uses narrow, empirically
informed uniform priors.

Whereas the papers of \citet{Oaks2012} and \citet{Hickerson2013} differ about
the cause and solution, they agree on the fundamental methodological point
about the model selection performed in \msb:
% The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
% on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       support for models with few divergence events shared across taxa. Thus,
       the primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}
This is not surprising given the rich statistical literature showing that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.
% We know that under broad uniform priors on divergence times, models with few
% divergence parameters will have greater marginal likelihoods relative to more
% parameter-rich models.
% Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
% for models with few divergence parameters is the greater marginal likelihoods
% of these models under vague uniform priors, relative to more parameter-rich
% models.
Under vague uniform priors on divergence times, models with more
divergence-time parameters integrate over \emph{much} greater parameter space
with low probability of producing the data, yet relatively high prior density
imposed by the uniformly distributed prior.
% By using such priors on divergence times, we are essentially telling the
% method to favor models with few divergence times even if they do not
% explain the data very well.
Thus, uniform priors on divergence times can impose a strong ``penalty'' for
divergence-time parameters, creating a strong preference for simple
models that are often of interest to biogeographers, even if these models do
not explain the data very well.
% It is important to note that this is not due to estimation error
% (i.e., this phenomenon is extrinsic to the numerical approximation machinery of
% \msb).
% Rather, the \emph{true} posterior will tend to support models with few
% divergence-time parameters under broad uniform priors on divergence times.
Such posterior support for simultaneous divergence, even if correct from the
perspective of Bayesian model choice, does not provide the biogeographical
insights that a researcher who employs \msb seeks to gain.
% Ideally, the estimated posterior probability of a simultaneous-divergence model
% can be interpreted as an estimate of the probability that this model is correct.
% However, when using uniform priors on divergence times, it might be better
% interpreted as an estimate of the probability that the simultaneous-divergence
% model cannot be completely ruled out as a possible explanation of the data.
% Note, this is a statistical issue, extrinsic to \msb, and does not question the
% soundness of the numerical approximation machinery of \msb.

% Alternatively, \citet{Hickerson2013} suggest the problem is the result of a
% numerical issue intrinsic to \msb, concluding the method's rejection algorithm
% is inefficient and will be biased toward models with fewer divergence-time
% parameters, because the parameter space of these models are more densely
% sampled relative to models with more divergence-time parameters.
% We agree that sampling error is present in all numerical Bayesian estimation
% methods, however, we show here that it is not a major contributer to the
% biases found by \citet{Oaks2012}.
% We present results here of analyses that, when combined with the results
% of \citet{Oaks2012}, strongly suggest that \msb prefers models with few
% divergence-time parameters, because they have greater likelihoods when
% averaged over broad uniform priors on divergences times.

% \citet{Oaks2012} suggest alternative prior probability distributions on
% divergence-times could increase the marginal likelihoods of models with more
% divergence-time parameters and thus reduce spurious support for models of
% temporally clustered divergences.
% Alternatively, \citet{Hickerson2013} present an approach that uses empirically
% informed uniform priors and Bayesian model-averaging in an attempt to accommodate
% uncertainty in selecting priors.
% In general, we agree with the use of Bayesian model averaging to obtain a
% posterior estimate marginalized over uncertainty in prior choice.
% However, we question whether adding an additional dimension of model choice
% that samples over empirically informed uniform priors is a fruitful solution
% for a model-choice method that is highly sensitive to priors.

\change{
Here, we discuss theoretical considerations for using empirically informed
priors for Bayesian model choice.
}
We then evaluate the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
\citet{Oaks2012}.
In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
made an error by mixing different units of time, which makes the results
presented in their response difficult to interpret (see Supporting Information
for details).
We avoid this error, but still find their approach to be biased toward
clustered divergence models.
Furthermore, the approach provides another means by which the method can
``escape'' models with large parameter space, which manifests in the preference
of models that exclude from consideration the true values of the model's
parameters.
\change{
Our results, show that it is difficult to choose a uniformly distributed prior
on divergence times that is broad enough to confidently contain the true values
of parameters while being narrow enough to avoid spurious support of models
with less parameter space.
}
We also explore the predictions of the alternative causes of this problem
proposed by \citet{Oaks2012} and \citet{Hickerson2013}.
We find the prior sensitivity of the marginal likelihoods is a likely
culprit,
and show that sampling error is not a major contributer to the biases found
by \citet{Oaks2012}.
Fortunately, \citet{Oaks2014dpp} has introduced a new method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without inhibiting the marginal likelihoods of models with
more divergence-time parameters, which increases the method's robustness and
power to detect temporal variation in divergences \citep{Oaks2014dpp}.

% \msb \citep{Huang2011} uses approximate Bayesian computation (ABC) to estimate
% the distribution of divergence times among co-distributed pairs of taxa.
% It approximates a posterior probability over models that range from a single
% divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
% to the fully generalized model in which each pair of taxa diverged at a
% unique time.
% % A full description of the model is given in \citet{Oaks2012}.
% % Frequently, the exact values of the divergence times are hard 
% % to determine because researchers typically lack precise knowledge 
% % of the rate at which substitutions occur.
% % The exact divergence time is therefore often viewed as a nuisance parameter,
% % and researchers focus on the number of divergence events.
% The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
% on the fundamental methodological point about the model selection performed in \msb:
% \begin{itemize}
%    \item The use of vague priors on the divergence-time parameters can lead to
%        support for models with few divergence events shared across taxa. Thus,
%        the primary inference enabled by the approach is very sensitive to the
%        priors on divergence times.
% \end{itemize}
% This is not surprising given the rich statistical literature that shows that
% marginal likelihoods are very sensitive to the priors used in Bayesian model
% selection
% \citep[e.g.,][]{Jeffreys1939,Lindley1957}.
% Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
% for models with few divergence parameters is the greater marginal likelihoods
% of these models under vague uniform priors, relative to more parameter-rich
% models.

% \change{
% Models with more divergence-time parameters integrate over \emph{much} greater
% parameter space with low probability of producing the data, yet relatively high
% prior density imposed by the uniformly distributed prior.
% % By using such priors on divergence times, we are essentially telling the
% % method to favor models with few divergence times even if they do not
% % explain the data very well.
% Thus, uniform priors on divergence times can impose a strong ``penalty'' for
% divergence-time parameters, creating a strong preference for simple
% models that are often of interest to biogeographers, even if these models do
% not explain the data very well.
% It is important to note that this is not due to estimation error
% (i.e., this phenomenon is extrinsic to the numerical approximation machinery of
% \msb).
% Rather, the \emph{true} posterior will tend to support models with few
% divergence-time parameters under broad uniform priors on divergence times.
% Such posterior support for simultaneous divergence, even if correct from the
% perspective of Bayesian model choice, does not provide the biogeographical
% insights that a researcher who employs \msb seeks to gain.
% % Ideally, the estimated posterior probability of a simultaneous-divergence model
% % can be interpreted as an estimate of the probability that this model is correct.
% % However, when using uniform priors on divergence times, it might be better
% % interpreted as an estimate of the probability that the simultaneous-divergence
% % model cannot be completely ruled out as a possible explanation of the data.
% % Note, this is a statistical issue, extrinsic to \msb, and does not question the
% % soundness of the numerical approximation machinery of \msb.
% }

% \citet{Hickerson2013} suggest the problem is the result of a numerical issue
% intrinsic to \msb, concluding the method's rejection algorithm is inefficient
% and will be biased toward models with fewer divergence-time parameters, because
% the parameter space of these models are more densely sampled relative to models
% with more divergence-time parameters.
% We agree that sampling error is present in all numerical Bayesian estimation
% methods, however, we show here that it is not a major contributer to the
% biases found by \citet{Oaks2012}.
% % We present results here of analyses that, when combined with the results
% % of \citet{Oaks2012}, strongly suggest that \msb prefers models with few
% % divergence-time parameters, because they have greater likelihoods when
% % averaged over broad uniform priors on divergences times.

% \citet{Oaks2012} suggest alternative prior probability distributions on
% divergence-times could increase the marginal likelihoods of models with more
% divergence-time parameters and thus reduce spurious support for models of
% temporally clustered divergences.
% Alternatively, \citet{Hickerson2013} present an approach that uses empirically
% informed uniform priors and Bayesian model-averaging in an attempt to accommodate
% uncertainty in selecting priors.
% In general, we agree with the use of Bayesian model averaging to obtain a
% posterior estimate marginalized over uncertainty in prior choice.
% However, we question whether adding an additional dimension of model choice
% that samples over empirically informed uniform priors is a fruitful solution
% for a model-choice method that is highly sensitive to priors.

% \change{
% In this paper, we discuss theoretical and practical considerations of using
% empirically informed priors for Bayesian model choice.
% }
% Furthermore, we evaluate the empirical Bayesian model-averaging approach of
% \citet{Hickerson2013} as a potential solution to the biases of \msb revealed by
% \citet{Oaks2012}.
% In their re-analysis of the dataset of \citet{Oaks2012}, \citet{Hickerson2013}
% made an error by mixing different units of time, which makes the results
% presented in their response difficult to interpret (see Supporting Information
% for details).
% Here, we avoid this error, but still find their approach to be biased toward
% clustered divergence models.
% Furthermore, the approach provides another means by which the method can
% ``escape'' models with large parameter space, which manifests in the preference
% of models that exclude from consideration the true values of the model's
% parameters.
% \change{
% Our results, show that it is difficult to choose a uniformly distributed prior
% on divergence times that is broad enough to confidently contain the true values
% of parameters while being narrow enough to avoid spurious support of models
% with less parameter space.
% }
% However, recent work shows more flexible probability distributions without a
% hard upper bound (e.g., gamma) can accommodate prior uncertainty in divergence
% times without inhibiting the marginal likelihoods of models with more
% divergence-time parameters, and as a result, increase the method's power to
% detect temporal variation in divergences
% \citep{Oaks2014dpp}.

\section{The potential implications of empirical Bayesian model choice}
\change{
% The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
% highly sensitive to the prior on divergence times.
\citet{Oaks2012} found that \msb would incorrectly support models of temporally
clustered divergences even when using a prior on divergence times that was
informed by the data being analyzed.
The main argument of \citet{Hickerson2013} is that the priors used by
\citet{Oaks2012} were not informative enough.
}
%
% \citet{Hickerson2013} repeatedly refer to the prior distributions used by
% \citet{Oaks2012} for divergence-time parameters as ``poorly selected.''
% However, this is misleading, as \citet{Oaks2012} discuss in detail how they
% selected their prior to reflect the large amount of uncertainty about the
% timing of divergences across all 22 of the taxa in their study (see section
% ``Specifying and simulating the joint prior'' of \citet{Oaks2012}).
% \citet{Oaks2012} further discuss how the use of uniform prior distributions in
% \msb for many of the model's parameters requires investigators to select broad
% priors to avoid excluding the truth \textit{a priori}, resulting in too much
% density in improbable regions of parameter space.
%
% \citet{Hickerson2013} suggest that \citet{Oaks2012} should have used their
% data to inform their prior on divergence times (i.e., an empirical Bayesian
% approach).
% However, \citet{Oaks2012} did use empirically informed priors to mimic
% empirical situations in which a large amount of prior information is available;
% they did so to assess the prior sensitivity of the method and to determine if
% uniform priors in such situations are narrow enough to avoid spurious support
% of models with few divergence-time parameters.
% The results of \citet{Oaks2012} and \citet{Hickerson2013} show the method is
% highly sensitive to the prior on divergence times.
% Furthermore, \citet{Oaks2012} found the method remained biased toward clustered
% divergences under the empirically informed priors.
%
% The main argument of \citet{Hickerson2013} is that the priors used by
% \citet{Oaks2012} were not informative enough.
They suggest a very narrow, highly informed uniform prior on divergence times
is necessary to avoid the method's preference for models with few
divergence-time parameters.
Such an empirical Bayesian approach to model selection raises some theoretical
and practical concerns, some of which were discussed by \citet{Oaks2012} (see
the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}); we expand on this here.

@@

\subsection{Practical concerns about empirically informed uniform priors for
    Bayesian model choice}
In addition to the theoretical concerns discussed above, there are practical
problems with using narrow, empirically informed, uniform priors.
% for a method that has already been shown to be biased toward models with less
% parameter space.
The results of Hickerson et al.'s (\citeyear{Hickerson2013}) reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa.
%, a major problem when using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the limit on the prior, because
some of the taxon pairs are expected to have diverged at times older than the
upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).

\change{
Hickerson et al.'s (\citeyear{Hickerson2013}) results that strongly prefer the
narrowest priors on divergence times (their $M_1$ and $M_2$) suggest their
approach is biased toward models with less parameter space, and as a
consequence, will estimate model-averaged posteriors dominated by models that
exclude true values of model's parameters.
}
We explored this possibility in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging
approach of \citet{Hickerson2013}, but set one of the prior models with a
uniform prior on divergence times that is unrealistically narrow, and almost
certainly excludes most, if not all, of the true divergence times of the 22
taxon pairs.
If small likelihoods of large models cause the method to prefer models with
less parameter space, we expect \msb will preferentially sample from this
incorrect model yielding a posterior that is incorrect (i.e., the
model-averaged posterior will be dominated by an incorrect model that excludes
the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

\subsubsection{Simulation-based assessment of Hickerson et al.'s
    (\citeyear{Hickerson2013}) model averaging over empirical priors}

@@

Even if we assume the gene divergence times are estimated without error,
Hickerson et al.'s (\citeyear{Hickerson2013}) argument only applies to one of
the three different priors used by \citet{Oaks2012}.
The narrowest prior on divergence times used by \citet{Oaks2012} ($U(0, 5)$)
closely mirrors the range of estimates of gene-divergence times if we assume
the same mutation rate and one generation per year (0--5 million years ago).
Applying Hickerson et al.'s (\citeyear{Hickerson2013}) sampling-probability
argument demonstrates this prior is densely populated with samples with large
numbers of divergence parameters with values younger than the estimated gene
divergence estimates.
Thus, if insufficient prior sampling is to blame for the bias, it should be
much reduced under the narrow prior on \divt{}.
However, the magnitude of the bias is very similar across all three priors
explored by \citet{Oaks2012}.
\citet{Hickerson2013} point out a case where the narrow prior performs
slightly better (panel L of Figures S32, S37, and S38 of \citet{Oaks2012}).
However, it is important to note that these results suffered from a bug
in \msb, and there are many cases after \citet{Oaks2012} corrected the 
bug where the narrow prior performs slightly worse (see panels D--J of
Figures 3 and S12).
